Predicting Evaluation Prices of Danish Real Estate Property

### 2019-08-27 Opsætningexam/DraftExam.tex
Updatelatex

\section{Data description \& Ethics}

\paragraph{Ethical considerations in the current research project\newline}

@@

\paragraph{Social and economic factors\newline}
Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and  
\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. These factors includes income, reported crime and level of completed education etc. These are transformed to into ratios, by taking the total population in a given municipality into account.

\subsection{Exclusion of outliers}
A few of the listed housing, have been for sale for over a decade. These are considered outliers, which are overly priced considering their characteristics. The outliers are excluded, because they would otherwise only contribute to a bias of overestimation. The total number of excluded housing are approximately 4000.  
\newline
\begin{tabular}{| c | c | c | c | c | c |} 
  \toprule
  \multicolumn{6}{|c|}{Danmark} \\ \hline
   & \multicolumn{2}{c|}{Sjælland} & \multicolumn{3}{c|}{Ikke Sjælland} \\ \hline
  Type/Region & Hovedstaden & Sjælland & Syddanmark & Midtjylland & Nordjylland \\
   \midrule 
   Villa & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
   Rækkehus & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
   Ejerlejlighhed & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
   Fritidsbolig & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
   Kolonihave & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
   Andelsbolig & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
   Landejendom & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
   Helårsgrund & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
   Fritidsgrund & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
   Villalejlighed & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
   Lystejendom & 470,67 & 404,95 & 460,93 & 407,24 & \\ 
    \bottomrule
\end{tabular}
\newline

>>>>

\section{Data Description \& Ethics}

\subsection{Ethical Considerations in the Current Research Project}

@@

\paragraph{Social and economic factors\newline}
Social and economic factors on municipality level is collected from \href{https://statistik.politi.dk/QvAJAXZfc/opendoc.htm?document=QlikApplication%2F2999_Public\%2FPublic_IndsatsResultater.qvw}{statistik.politi.dk} and  
\href{https://www.dst.dk/da/Statistik/emner/befolkning-og-valg}{Danmarks Statistik} respectively. These factors includes income, reported crime and level of completed education etc. These are transformed to into ratios, by taking the total population in a given municipality into account.   
\subsection{Merging Data}

\subsection{Data Cleaning}
A few of the listed housing, have been for sale for over a decade. These are considered outliers, which are overly priced considering their characteristics. The outliers are excluded, because they would otherwise only contribute to a bias of overestimation. The total number of excluded housing are approximately 4000.

\subsection{Describtive Statistics}
\subsubsection{The Dataset}
\subsubsection{Selecting Features}

\begin{tabular}{| c | c | c | c | c | c |} 
  \toprule
  \multicolumn{6}{|c|}{Danmark} \\ \hline
   & \multicolumn{2}{c|}{Sjælland} & \multicolumn{3}{c|}{Ikke Sjælland} \\ \hline
  Type/Region & Hovedstaden & Sjælland & Syddanmark & Midtjylland & Nordjylland \\
   \midrule 
   Villa & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
   Rækkehus & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
   Ejerlejlighhed & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
   Fritidsbolig & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
   Kolonihave & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
   Andelsbolig & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
   Landejendom & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
   Helårsgrund & 470,67 & 404,95 & 460,93 & 407,24 & \\ \hline
   Fritidsgrund & 482,30 & 463,94 & 455,87 & 449,54 & \\ \hline
   Villalejlighed & 513,36 & 459,67 & 503,62 & 461,96 & \\ \hline
   Lystejendom & 470,67 & 404,95 & 460,93 & 407,24 & \\ 
    \bottomrule
\end{tabular}
\newline
